---
title: "R Project 1 - Hello R"
author: "Robert Tamayo IV"
date: "[NOT] Due Fed 3rd"
output: 
  html_document: 
    highlight: kate
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and does not explicitly say how many columns are there. If there are any, I assume there are the three columns for the variables, the dataset which indicates which dataset the data is from, x which indicates the x-values, and y which indicates the y-values.

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, remember to clean up the narrative by removing these instructions.)

This is the plot for the star dataset.

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

This is the correlation between x and y for the star data. This value is 0.0015 units higher than the correlation for the dino data.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

This is the plot for the circle dataset.

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

This is the correlation between x and y for the circle data. This value is 0.0038 units lower than the correlation for the dino data.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) # facet the dataset variable, in 3 cols theme(legend.position = "none")
```

```{r}
datasaurus_dozen %>% group_by(dataset) %>% 
summarize(r = cor(x, y)) %>% print(13)
```